---
title: "p8105_hw6_rw3033"
output: github_document
---
# Question 1
```{r}
# Libraries
library(dplyr)
library(broom)
library(purrr)
library(ggplot2)
```


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
# Perform 5000 bootstrap samples and fit the linear model
bootstrap_results = weather_df |>
  modelr::bootstrap(n = 5000, id = "bootstrap_id") |>
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    # R^2
    r_squared = map_dbl(models, function(model) glance(model)[["r.squared"]]),
    # log(beta0 * beta1)
    log_beta_product = map_dbl(models, function(model) {
      coefs <- tidy(model)[["estimate"]]
      log(coefs[1] * coefs[2])
    })
  )

# CI of the bootstrap results
ci_results = bootstrap_results |>
  summarise(
    r_squared_lower = quantile(r_squared, 0.025),
    r_squared_upper = quantile(r_squared, 0.975),
    log_beta_product_lower = quantile(log_beta_product, 0.025),
    log_beta_product_upper = quantile(log_beta_product, 0.975)
  )
```


```{r}
# Plot the distributions
# R-squared distribution
ggplot(bootstrap_results, aes(x = r_squared)) +
  geom_histogram() +
  labs(title = "Bootstrap Distribution of R-squared",
       x = "R-squared",
       y = "Frequency")

# Log(beta0 * beta1) distribution
ggplot(bootstrap_results, aes(x = log_beta_product)) +
  geom_histogram() +
  labs(title = "Bootstrap Distribution of log(beta0 * beta1)",
       x = "log(beta0 * beta1)",
       y = "Frequency")
```
Description:
The bootstrap distribution of R^2 is slightly right-skewed, with most values concentrated between 0.89 and 0.92 and a peak near 0.91, indicating a strong and consistent model fit across samples. The distribution of log(beta0 * beta1) is symmetric and bell-shaped, centered around 2.00, suggesting stable relationships between the intercept and slope across resamples.


# Problem 2



