---
title: "p8105_hw6_rw3033"
output: github_document
---
# Libraries
```{r}
library(dplyr)
library(broom)
library(purrr)
library(ggplot2)
library(tidyr)
library(modelr)
```


# Question 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
# Perform 5000 bootstrap samples and fit the linear model
bootstrap_results = weather_df |>
  modelr::bootstrap(n = 5000, id = "bootstrap_id") |>
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    # R^2
    r_squared = map_dbl(models, function(model) glance(model)[["r.squared"]]),
    # log(beta0 * beta1)
    log_beta_product = map_dbl(models, function(model) {
      coefs <- tidy(model)[["estimate"]]
      log(coefs[1] * coefs[2])
    })
  )

# CI of the bootstrap results
ci_results = bootstrap_results |>
  summarise(
    r_squared_lower = quantile(r_squared, 0.025),
    r_squared_upper = quantile(r_squared, 0.975),
    log_beta_product_lower = quantile(log_beta_product, 0.025),
    log_beta_product_upper = quantile(log_beta_product, 0.975)
  )
```


```{r}
# Plot the distributions
# R-squared distribution
ggplot(bootstrap_results, aes(x = r_squared)) +
  geom_histogram() +
  labs(title = "Bootstrap Distribution of R-squared",
       x = "R-squared",
       y = "Frequency")

# Log(beta0 * beta1) distribution
ggplot(bootstrap_results, aes(x = log_beta_product)) +
  geom_histogram() +
  labs(title = "Bootstrap Distribution of log(beta0 * beta1)",
       x = "log(beta0 * beta1)",
       y = "Frequency")
```
Description:
The bootstrap distribution of R^2 is slightly right-skewed, with most values concentrated between 0.89 and 0.92 and a peak near 0.91, indicating a strong and consistent model fit across samples. The distribution of log(beta0 * beta1) is symmetric and bell-shaped, centered around 2.00, suggesting stable relationships between the intercept and slope across resamples.


# Problem 2
```{r}
# Import data
homicide_df = read.csv("~/Desktop/BIST8105/HW/p8105_hw6_rw3033/homicide-data.csv")

# Data cleaning
# Create the city_state variable
clean_homicide_df = homicide_df |>
  mutate(city_state = paste0(city, ", ", state))|>
  mutate(
    solved_homicides = ifelse(
      disposition %in% c("Closed without arrest", "Open/No arrest"), 0, 1
    )
  ) |>
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) |>
  filter(victim_race %in% c("White", "Black")) |>
  mutate(victim_age = as.numeric(victim_age))
```

```{r}
# Filter the dataset for Baltimore, MD
baltimore_data = clean_homicide_df |>
  filter(city_state == "Baltimore, MD")

# Fit the logistic regression model
baltimore_model = glm(
  solved_homicides ~ victim_age + victim_sex + victim_race,
  family = binomial(link = "logit"),
  data = baltimore_data
)

# Summarize the model
baltimore_model_summary = broom::tidy(
  baltimore_model,
  conf.int = TRUE,
  exponentiate = TRUE
)

# The estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims
baltimore_model_summary |>
  filter(term == "victim_sexMale") |>
  select(term, estimate, conf.low, conf.high)
```


```{r}
# Fit a glm for each city and extract ORs and CIs
city_or_ci = clean_homicide_df |>
  group_by(city_state) |>
  nest() |>
  mutate(
    model = purrr::map(data, ~ glm(
      solved_homicides ~ victim_age + victim_sex + victim_race,
      family = binomial(link = "logit"),
      data = .x
    )),
    tidy_model = purrr::map(model, ~ broom::tidy(.x, conf.int = TRUE, exponentiate = TRUE))
  ) |>
  unnest(tidy_model) |>
  filter(term == "victim_sexMale") |>
  select(city_state, estimate, conf.low, conf.high)
```

```{r}
# Plot the results
city_or_ci_plot = city_or_ci |>
  mutate(city_state = reorder(city_state, estimate)) |>
  ggplot(aes(x = estimate, y = city_state)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high)) +
  labs(
    title = "Adjusted Odds Ratios for Solving Homicides by City",
    x = "Adjusted Odds Ratio (Male vs Female Victims)",
    y = "City",
    caption = "Error bars represent 95% confidence intervals"
  ) +
  theme_minimal(base_size = 8)

print(city_or_ci_plot)
```
Comment:


# Problem 3

```{r}
# Import data
birthweight_df = read.csv("~/Desktop/BIST8105/HW/p8105_hw6_rw3033/birthweight.csv", na = c("NA", ".", "", "null", "-"))


# Data cleaning
birthweight_df = birthweight_df |>
  mutate(
    fincome = as.numeric(fincome), 
    wtgain = as.numeric(wtgain), 
    gaweeks = as.numeric(gaweeks) 
  )|>
  drop_na()
```


```{r}
# Fit the regression model
model_1 = lm(
  bwt ~ gaweeks + babysex + mheight + wtgain + smoken,
  data = birthweight_df
)

# Add predictions and residuals to the dataset
birthweight_predictions = birthweight_df |>
  add_predictions(model_1) |>
  add_residuals(model_1)
```
Comment:
My model is bwt=β0+β1(gaweeks)+β2(babysex)+β3(mheight)+β4(wtgain)+β5(smoke)+ϵ.
This model is based on a hypothesized structure for the factors that underly birthweight.

```{r}
# Plot residuals vs fitted values
residuals_plot = ggplot(birthweight_predictions, aes(x = pred, y = resid)) +
  geom_point() + 
  labs(
    title = "Residuals vs Fitted Values",
    x = "Fitted Values (Predicted Birthweight)",
    y = "Residuals"
  ) +
  theme_minimal()

print(residuals_plot)
```

```{r}
# Plot RMSE distributions
cv_results <- cv_folds |> 
  mutate(
    model_1 = map(train, ~ lm(bwt ~ gaweeks + babysex + mheight + wtgain + smoken, data = .x)),
    model_2 = map(train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    model_3 = map(train, ~ lm(bwt ~ bhead + blength + babysex + bhead * blength + bhead * babysex + blength * babysex + bhead * blength * babysex, data = .x)),
    model_1_rmse = map2_dbl(model_1, test, ~ rmse(.x, .y)),
    model_2_rmse = map2_dbl(model_2, test, ~ rmse(.x, .y)),
    model_3_rmse = map2_dbl(model_3, test, ~ rmse(.x, .y))
  ) |> 
  select(model_1_rmse, model_2_rmse, model_3_rmse) |> 
  pivot_longer(
    cols = everything(),
    names_to = "model",
    values_to = "rmse"
  )
```

```{r}
# Plot
cv_results |> 
  ggplot(aes(x = model, y = rmse)) +
  geom_boxplot() +
  labs(
    title = "Cross-Validated RMSE for Birthweight Models",
    x = "Model",
    y = "RMSE"
  ) +
  theme_minimal()
```
Comment:
The boxplot shows the cross-validated RMSE (root mean squared error) for three models predicting birthweight. Model 1 (Proposed Model) has the highest RMSE (~450) with relatively narrow variability, indicating poorer predictive accuracy but consistent performance across cross-validation splits. Model 2 (Main Effects) achieves lower RMSE (~400) with slightly more variability, suggesting improved predictive accuracy from the inclusion of gestational age and birth length. Model 3 (Interaction Model) has the lowest RMSE (~300) and greater variability, reflecting superior predictive performance but potential sensitivity to data splits due to its complexity. Overall, Model 3 provides the best predictions, but its added complexity should be carefully considered.
